### 2016-09-30 architecture.tex
"other examples" (one was just shown)
Hashing is useful for any dict, not just caching

Descending further down into the expression tree yields the full expression. For
example, the next child node (given by \texttt{expr.args[0]}) is
\texttt{2}. Its class is \texttt{Integer}, and it has an empty \texttt{args}
tuple, indicating that it is a leaf node.
\begin{verbatim}
>>> expr.args[0]
2
>>> type(expr.args[0])
<class 'sympy.core.numbers.Integer'>
>>> expr.args[0].args
()
\end{verbatim}
Symbols or symbolic constants, like $e$ or $\pi$, are examples of
leaf nodes.
\begin{verbatim}
>>> exp(1)
E
>>> exp(1).args
()
>>> x.args
()
\end{verbatim}

@@

Another important property of SymPy expressions is that they are immutable.
This simplifies the design of SymPy by allowing expression interning. It also
enables expressions to be hashed, which is used to implement caching in SymPy.

>>>>

Descending further down into the expression tree yields the full expression. For
example, the next child node (given by \texttt{expr.args[0]}) is
\texttt{2}. Its class is \texttt{Integer}, and it has an empty \texttt{args}
tuple, indicating that it is a leaf node.
\begin{verbatim}
>>> expr.args[0]
2
>>> type(expr.args[0])
<class 'sympy.core.numbers.Integer'>
>>> expr.args[0].args
()
\end{verbatim}
Symbols or symbolic constants, like $e$ or $\pi$, are other examples of
leaf nodes.
\begin{verbatim}
>>> exp(1)
E
>>> exp(1).args
()
>>> x.args
()
\end{verbatim}

@@

Another important property of SymPy expressions is that they are immutable.
This simplifies the design of SymPy by allowing expression interning. It also
enables expressions to be hashed, which allows expressions to be used as keys
in Python dictionaries, and is used to implement caching in SymPy.
